### 2016-01-29 featureImagesTable.tex
ENH:  More.

\begin{table}[!htb]
  \centering
  \begin{tabular*}{0.65\textwidth}{@{\extracolsep{\fill}} ll}
    \multicolumn{1}{c}{\textbf{Feature type}} & \multicolumn{1}{c}{\textbf{Image source}} \\
    \toprule
    \midrule
    \multicolumn{2}{c}{\textbf{Intensities}} \\
    \midrule
    normalized/preprocessed & FLAIR, T1, and T2 \\
    \midrule
    \multicolumn{2}{c}{\textbf{Symmetric template}} \\
    \midrule
    template difference & FLAIR, T1, and T2 \\
    contralateral difference & FLAIR, T1, and T2 \\
    location indices & FLAIR, T1, and T2 \\
    \midrule
    \multicolumn{2}{c}{\textbf{Segmentation probabilities}} \\
    \midrule
    $Pr$(cerebrospinal fluid) & T1 \\
    $Pr$(gray matter) & T1 \\
    $Pr$(white matter) & T1 \\
    $Pr$(deep gray matter) & T1 \\
    $Pr$(brain stem) & T1 \\
    $Pr$(cerebellum) & T1 \\
    \midrule
    \multicolumn{2}{c}{\textbf{Distance maps}} \\
    \midrule
    cerebrospinal fluid & T1 brain segmentation \\
    gray matter & T1 brain segmentation \\
    deep gray matter & T1 brain segmentation \\
    whole brain & T1 brain segmentation \\
    \midrule
    \multicolumn{2}{c}{\textbf{Neighborhood statistics}} \\
    \midrule
    mean & FLAIR, T1, and T2 \\
    standard deviation & FLAIR, T1, and T2 \\
    skewness & FLAIR, T1, and T2 \\
    \midrule
    \bottomrule
  \end{tabular*}
 \label{table:indices}
 \caption{List of feature images used for Stage 1 of the proposed white matter
          hyperintensity segmentation framework.}
\end{table}

>>>>

\begin{table}[!htb]
  \centering
  \begin{tabular*}{0.85\textwidth}{@{\extracolsep{\fill}} lll}
    \multicolumn{1}{c}{\textbf{Feature type}} & \multicolumn{1}{c}{\textbf{Image source}} & \multicolumn{1}{c}{\textbf{Name}} \\
    \toprule
    \midrule
    \multicolumn{3}{c}{\textbf{Intensities}} \\
    \midrule
    normalized/preprocessed & FLAIR, T1, and T2 & \texttt{Preprocessed} \\
    \midrule
    \multicolumn{3}{c}{\textbf{Symmetric template}} \\
    \midrule
    template difference & FLAIR, T1, and T2 & \texttt{SymmetricTemplateDifference}\\
    contralateral difference & FLAIR, T1, and T2 & \texttt{ContralateralDifference}\\
    template location indices & FLAIR, T1, and T2 & \texttt{TemplateIndicesWarped}\\
    \midrule
    \multicolumn{3}{c}{\textbf{Segmentation probabilities}} \\
    \midrule
    $Pr$(cerebrospinal fluid) & T1 & \texttt{BrainSegmentationPosteriors1}\\
    $Pr$(gray matter) & T1 & \texttt{BrainSegmentationPosteriors2}\\
    $Pr$(white matter) & T1 & \texttt{BrainSegmentationPosteriors3}\\
    $Pr$(deep gray matter) & T1 & \texttt{BrainSegmentationPosteriors4}\\
    $Pr$(brain stem) & T1 & \texttt{BrainSegmentationPosteriors5}\\
    $Pr$(cerebellum) & T1 & \texttt{BrainSegmentationPosteriors6}\\
    \midrule
    \multicolumn{3}{c}{\textbf{Distance maps}} \\
    \midrule
    cerebrospinal fluid & T1 brain segmentation & \texttt{NormalizedCsfDistance}\\
    gray matter & T1 brain segmentation & \texttt{NormalizedGmDistance}\\
    deep gray matter & T1 brain segmentation & \texttt{NormalizedDeepGmDistance}\\
    whole brain & T1 brain segmentation & \texttt{NormalizedMaskDistance}\\
    \midrule
    \multicolumn{3}{c}{\textbf{Neighborhood statistics}} \\
    \midrule
    mean & FLAIR, T1, and T2 & \texttt{NeighborhoodMean}\\
    standard deviation & FLAIR, T1, and T2  & \texttt{NeighborhoodSigma}\\
    skewness & FLAIR, T1, and T2  & \texttt{NeighborhoodSkewness}\\
    \midrule
    \bottomrule
  \end{tabular*}
 \label{table:indices}
 \caption{List of feature images used for Stage 1 of the proposed white matter
          hyperintensity segmentation framework.  These feature images encompass
          salient location and intensity information used for voxelwise identification
          of white matter hyperintensities in TBI.  The column on the right provides
          the names used in the software developed for this methodology and
          facilitates discussion of the results (cf Figure 2).
          }
\end{table}

### 2016-01-29 results.Rmd
ENH:  More.

As mentioned previously, segmentation of white matter hyperintensities in traumatic brain
injury cohorts is a much more difficult problem than

![Average \texttt{MeanDecreaseAccuracy} plots generated from the creation of all 24 random
forest models for both Stage 1 and Stage 2 during the leave-one-out evaluation.  These plots
are useful in providing a quantitative assessment of the predictive importance of each feature.
The error bars provide the $95^{th}$ percentile (i.e., $1.96 \times \sigma$) and illustrate the
stability of the feature importance across the leave-one-out models.](Figures/averageLeaveOneOut.png)

To calculate this quantity for a single feature from a single random forest model, the
decrease in prediction accuracy produced by omitting the specified feature is calculated
during the out-of-bag phase of model creation.

During the out-of-bag error calculation stage of the random forest model creation, the
decrease in prediction accuracy with the omission of a single feature or variable is
tracked and averaged. Those features which have the greatest decrease in mean accuracy are
considered to be the most discriminative. In this work, we do not use these measurements for
feature pruning.

>>>>

After performing the leave-one-out evaluation described at the end of the previous section,
we calculated the \texttt{MeanDecreaseAccuracy} feature values for each of the 24 subjects $\times$
2 models per subject $=48$ total models.  This measure (per feature, per model) is calculated
during the out-of-bag phase of the random forest model construction and quantifies the decrease
in prediction accuracy from omitting the specified feature.  In other words, this quantity
helps determine the importance of a particular feature and, although we save such
efforts for future work, this information provides us with guidance for future feature
pruning and/or additions.

The resulting rankings for both Stages are given in Figure 2 where the values for the
separate stages are averaged over the entire corresponding model set.  In addition, we
track the variance for each feature over all models to illustrate the stability of
the chosen features during the evaluation.  This latter information is illustrated as
horizontal errors bars providing the $95^{th}$ percentile (i.e., $1.96 \times \sigma$).

One can also use these measurements as a type of sanity check.  For example, from the Stage
1  plot, one can see that the \texttt{MeanDecreaseAccuracy} values for the location indices in the
anterior-posterior direction (i.e., \texttt{TemplateIndicesWarped1}) are greater than
those for either the inferior-superior (i.e., \texttt{TemplateIndicesWarped0}) or the
left-right (i.e., \texttt{TemplateIndicesWarped0}) directions in the space of the symmetric
template.  This is intuitive since, as discussed previously, manifestation of TBI white
matter hyperintensities can often be confused with higher intensities at the
periventricular caps in normal subjects [@Neema:2009aa] whereas there does not seem to
be contralateral bias in manifestation of white matter hyperintensities in TBI [@reference].
Additionally, it is interesting to see that the top two performing
A couple of  other interesting

![Average \texttt{MeanDecreaseAccuracy} plots generated from the creation of all 24 random
forest models for both Stage 1 and Stage 2 during the leave-one-out evaluation.  These plots
are useful in providing a quantitative assessment of the predictive importance of each feature.
The horizontal error bars provide the $95^{th}$ percentile (i.e., $1.96 \times \sigma$) and illustrate the
stability of the feature importance across the leave-one-out models.](Figures/averageLeaveOneOut.png)

![LLV](Figures/llvAndDice.png)
